Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2019-04-17 awipev-CO2.Rmd
AT/CT serie from 07-2018 to 11-2018 updated with flags 1

- 2015-11-18
- 2016-07-28
- 2016-09-29
- 2016-11-17
- 2016-11-23
- 2016-12-29
- 2017-01-19
- 2017-05-04
- 2018-04-26
- 2018-05-04
- 2018-05-16
- 2018-05-25
- 2018-06-22
- 2018-06-30
- 2018-07-27

@@

- 2015-08-06
- 2015-08-13
- 2016-05-12
- 2016-05-16
- 2016-06-16
- 2016-07-28
- 2016-09-08
- 2016-10-27
- 2016-11-17
- 2017-01-19
- 2017-03-02
- 2017-04-27
- 2017-09-17
- 2018-04-26
- 2018-05-04
- 2018-05-12
- 2018-05-25
- 2018-06-30

```{r SNAPO, echo=FALSE, message= FALSE, warning=FALSE}
# use the df at_ct for mean and sd
# creat a new df to calculate the diff between replicate
 diff <- d %>%
    group_by(datetime) %>%
   dplyr::select(datetime, at, ct)%>%   
   dplyr::mutate(at_diff = abs(at - lag(at)),
                 ct_diff = abs(ct - lag(ct)))

>>>>

- 2015-11-18
- 2016-07-28
- 2016-09-29
- 2016-11-17
- 2016-11-23
- 2016-12-29
- 2017-01-19
- 2017-05-04
- 2017-08-31
- 2018-04-26
- 2018-05-04
- 2018-05-16
- 2018-05-25
- 2018-06-22
- 2018-06-30
- 2018-07-27
- 2018-07-20
- 2018-08-03
- 2018-08-10
- 2018-08-31
- 2018-09-07
- 2018-09-14
- 2018-09-21
- 2018-09-28
- 2018-10-05
- 2018-10-12
- 2018-10-19
- 2018-10-26
- 2018-11-02
- 2018-11-09
- 2018-11-16
- 2018-11-23

@@

- 2015-08-06
- 2015-08-13
- 2016-05-12
- 2016-05-19
- 2016-06-16
- 2016-07-28
- 2016-09-08
- 2016-10-27
- 2016-11-17
- 2017-01-19
- 2017-03-02
- 2017-04-27
- 2017-09-14
- 2018-04-26
- 2018-05-04
- 2018-05-12
- 2018-05-25
- 2018-06-30
- 2018-07-20
- 2018-08-03
- 2018-08-31
- 2018-09-07
- 2018-09-14
- 2018-09-28
- 2018-10-05
- 2018-10-12
- 2018-10-19
- 2018-10-26
- 2018-11-02
- 2018-11-09
- 2018-11-16
- 2018-11-23
```{r SNAPO, echo=FALSE, message= FALSE, warning=FALSE}
# use the df at_ct for mean and sd
# creat a new df to calculate the diff between replicate
 diff <- d %>%
    group_by(datetime) %>%
   dplyr::select(datetime, at, ct)%>%   
   dplyr::mutate(at_diff = abs(at - lag(at)),
                 ct_diff = abs(ct - lag(ct)))
